SAT Competition 2020\tnoteref{title}

### 2021-05-06 paper/main.tex
Explain table underline; beautify other table

\caption{Top 10 Solvers in Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}

@@

VBS2 highlights as first \solver{Kissat-sat}. Its leading \SI{32.9}{\percent} of total is a bit harder to 
interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
by solving \SI{32.9}{\percent} of the solved instances in the best observed time
and no others. But we know, thanks to its VBS1, that \solver{Kissat-sat} solved \SI{9.8}{\percent}
of the solved instances in the best observed time (and some others).
A solver can also score \SI{32.9}{\percent} of VBS2 total by solving all the solved instances,
but always being roughly 3 times slower than the VBS. 
\solver{Kissat-sat} lies obviously somewhere between these two extremes.

@@

\begin{table}
\centering\small
\begin{tabulary}{\linewidth}{cccL}
\bf k & \bf Time (s) & \bf Solved & \bf Best Schedule \\
\hline
1 & 5000 & 264 & \{ \solver{Kissat-sat} \}\\
2 & 2500 & 278 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \}\\
3 & 1666 & 272 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids} \} \\
4 & 1250 & 262 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids}, \phantom{\{ }\solver{Maple-alluip-trail} \}\\ 
5 & 1000 & 253 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids}, \phantom{\{ }\solver{Maple-alluip-trail}, \solver{CaDiCaL-alluip} \}\\
\end{tabulary}
\caption{Schedules that maximize the number of solved Main track instances for $k \in \{1, \dots, 5\}$ solvers among which $5000$ seconds are split uniformly.}
\label{tab:MainUniformTimeSplit}
\end{table}

>>>>

\caption{Top 10 Solvers in Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver.
Three awardees per track underlined.}

@@

The metric VBS2 identifies as the best solver \solver{Kissat-sat}. Its leading score of \SI{32.9}{\percent} of the total
is a bit harder to interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
by solving \SI{32.9}{\percent} of the solved instances in the best observed time
and no others. But we know, thanks to its VBS1, that \solver{Kissat-sat} solved \SI{9.8}{\percent}
of the solved instances in the best observed time (and some others).
A solver can also score \SI{32.9}{\percent} of VBS2 total by solving all the solved instances,
but always being roughly 3 times slower than the VBS. 
\solver{Kissat-sat} lies (obviously) somewhere between these two extremes.

@@

\begin{table}
\centering\small
\begin{tabulary}{\linewidth}{cccL}
\bf k & \bf Time\,(s) & \bf Solved & \bf Best Schedule \\
\hline
1 & 5000 & 264 & \{ \solver{Kissat-sat} \}\\
2 & 2500 & 278 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \}\\
3 & 1666 & 272 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids} \} \\
4 & 1250 & 262 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids}, \phantom{\{ }\solver{Maple-alluip-trail} \}\\ 
5 & 1000 & 253 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids}, \phantom{\{ }\solver{Maple-alluip-trail}, \solver{CaDiCaL-alluip} \}\\
\end{tabulary}
\caption{Schedules that maximize the number of solved Main track instances for $k \in \{1, \dots, 5\}$ solvers among which $5000$ seconds are split uniformly.}
\label{tab:MainUniformTimeSplit}
\end{table}
